# Correlations 
## r-code for pearson's correlation
```{r}
cor(data$x, data$y)
```
## r-code for spearman's rho 
```{r}
cor(data$x, data$y, method="spearman")
```


# Examples
## pearson's r
1). A reseracher wants to find the correlation between the occurance of BETA waves (Hz), 
as time increaees when a particpant beings to sleep
```{r}
BETA_Wave <-c(654, 600, 546, 492, 438, 325)
time <- c(1, 2, 3, 4, 5, 6)
cbind.data.frame(time, BETA_Wave) -> data
```

```{r}
cor(data$time, data$BETA_Wave)
```

### Interpreation 
As the correlation value is -0.988, there is a strong negative trend between time and BETA_waves.

## Spearman's rho 
A teacher wants to evaulate her classes ranking on the spelling bee, and how early those students arrive to class.
```{r}
time <- c(60, 120, 135, 200, 2400)
ranking <- c(1, 2, 6 ,5 ,10)
cbind.data.frame(time, ranking) -> spelling
```

```{r}
cor(spelling$time, spelling$ranking, method=)
```
### Interpreation
There is a storng postiive relatonship between time late and score.
