# ANOVA - Rcode 
## Creating a 'long table'
```{r}
library(tidyr)
data_long <- gather(data_frame)
print(data_long)
```

## ANVOA function 
```{r}
anova <- aov(dv~iv
    data=managerData )
```

## Tukey HSD 
```{r}
TukeyHSD(anovaMODEL)
```

## Effect Sizes
```{r}
library(lsr)
etaSquared(anovaMODEL)
```

## General NHST-test code 
```{r}
alpha = groups * 0.05
#Set critical area as 0.05 * crtitcal area. 
qt(alpha, df)
#note if looking for greater do 0.95, if less do 0.05, (p's/alphas are probablity scores)
#nomral q (not needed usually)
qnorm(alpha)
```
```{r}
pt(t-stat, df, lower.tail = TRUE/FALSE)
# set lower.tail to value needed 
# if two tail is needed use this trick (notice the negative out front)
pt(-t-stat, df) + pt(t-stat, df, lower.tail = FALSE)
```


# Example
An immimmunologist wants to measure the difference in white blood cell count with
various different dieases. (measured in ppm) He does this with 5 different patietns per
group.

## Data 
```{r}
common_cold <-c(4.503, 5.102, 4.20, 4.404, 2.034 )
influenza <-c(6.050, 4.450, 8.505, 6.605, 4.0500)
pneumonia <-c(7.060, 5.403, 9.493, 4.394, 6.505)
disease_data <- cbind.data.frame(common_cold, influenza, pneumonia)
```

## Long table 

```{r}
library(tidyr)
disease_long = gather(disease_data)
disease_long
table(disease_long)
```
## ANOVA test
```{r}
anova_model <- aov(value~key, data=disease_long)
summary(anova_model)
```

## Intepreation, as the p-value is greater than 0.05, and the F value is greater than the critical value, there is a  
sigfigant reusult across all results

## HSD testing
```{r}
TukeyHSD(anova_model)
```
The greatest difference is between the pneumonia and infeluenze group, with a p-value of 0.08

## Effect Sizes
```{r}
library(lsr)
etaSquared(anova_model)
```